The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
conc edits

<!--QW: I am not very happy with this paragraph, but it's a start -->
Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement. 
Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks. It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data. -->

Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:

1. How do social phenotypes vary across social scales and differentially
influence fitness? Are some temporal or social scales better predictors for
different fitness metrics?
2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?
3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?

In summary, blah blah

>>>>

<!-- Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks incorporated high resolution GPS telemetry data and spatial landcover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore (e.g., number of observations, sociality across space
and time) are ones that can be observed as has traditionally been done. Thus, we
highlight ways in which scale ought to be considered for both observed and
remotely-sensed data when building social networks. Furthermore, GPS telemetry
data provides a link between large scale landscape properties and fine scale
social interactions as animal movement occurs across the landscape, and when
taken into account with multiple individuals can indicate association patterns.
Thus, a layer incorporating relocation data could be a great boon linking
spatial and social layer in multilayer networks.
<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks. It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data. -->

Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lens of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:

1. How do social phenotypes vary across social, temporal, and spatial scales and
differentially influence fitness? Are some scales better predictors for
different fitness metrics?
2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?
3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?

<!-- In summary, blah blah  -->
